\LARGE \bf Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-14 09-30-2014]

### 2014-10-02 paper.tex
author list attributions

\author{Michael Laskey, Zoe McCarthy, Jeff Mahler, Florian T. Pokorny, Sachin Patil,\\ Jur Van Den Berg,  Danica Kragic, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space

>>>>

\author{Michael Laskey$^1$, Zoe McCarthy$^1$, Jeff Mahler$^1$, Florian T. Pokorny$^3$, Sachin Patil$^1$,\\ Jur Van Den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{mdlaskey, zmccarthy, jmahler, sachinpatil, pabbeel\}@berkeley.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\tt\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
\thanks{$^3$Computer Vision and Active Perception Lab, Centre for Autonomous Systems, School of Computer Science and Communication, KTH Royal Institute of Technology, Stockholm, Sweden {\tt\small \{fpokorny, dani\}@kth.se}}%
\thanks{$^4$Google; Amphitheatre Parkway, Mountain View, CA 94043, USA {\tt\small jurvandenberg@gmail.com}}%
}
